Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-16 paper.tex
Small fix
Updated the file directory of figures user/item factors

Neuroinformatics pipelines are generally iterated on data coming from 10 to 
1,000 subjects, possibly with subtle input parameter variations to 
adjust specific data acquisition conditions. Subject data often capture 
anatomical and functional characteristics of their brain, for instance through
Magnetic Resonance Imaging (MRI) or Electroencephalography (EEG). The number of files 
associated with a subject may vary, and these files may also be of 
different sizes. Typical data processing times range from 15 minutes to 
15 hours per subject, with input ranging from 100~MB to 15~GB per subject, and 
outputs ranging from 1~GB to 500~GB.

@@

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
\caption{The three subject latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
\label{fig:userfactors}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
\caption{The three file latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
\label{fig:itemfactors}
\end{figure}

>>>>

Neuroinformatics pipelines are generally iterated on data coming from 10 to 
1,000 subjects, possibly with subtle input parameter variations to 
adjust specific data acquisition conditions. Subject data often capture 
anatomical and functional characteristics of their brain, for instance through
Magnetic Resonance Imaging (MRI) or Electroencephalography (EEG). The number of input files 
associated with a subject may vary, and these files may also be of 
different sizes. Typical data processing times range from 15 minutes to 
15 hours per subject, with input ranging from 100~MB to 15~GB per subject, and 
outputs ranging from 1~GB to 500~GB.

@@

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{figures/5i-3f-ALS-r1-08-userFactors.pdf}
\caption{The three subject latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
\label{fig:userfactors}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{figures/5i-3f-ALS-r1-08-itemFactors.pdf}
\caption{The three file latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
\label{fig:itemfactors}
\end{figure}
